### 2018-07-02 Reviews/Response2.tex
Prepared revision and resubmitted to journal

\opening{Dear Dr. Aseda}
Thank you very much for your consideration of our manuscript and for the opportunity to submit a revised version. We made several changes to the manuscript based on the reviewers' comments. More prominently, we \dots

@@

@@

{\color{blue} Habitat and environmental characteristics of the basing and fringe mangroves are described in the Mathrials and Methods section. Here in the introduction, we are describing the main motivation of the study and therefore it is not the most appropriate place to describe the study site. Figure 1 is mentioned in the text in the Methods section.}

@@

@@

{\color{blue} The rationale is presented in the introduction, where we mention that we use analyses of the structure and composition of the clay minerals to help in determining the origin of the stored carbon.}

@@

{\color{blue} Sorry for the confusion. In the ANOVA we didn't compare four categorical zones as the reviewer thought, but only the two groups of mangrove types: fringe and basin. Therefore the Tukey post-hoc test is not needed. }

@@

{\color{blue} This is inferred by simply multiplying bulk density by \% organic carbon. Also, you can reach this conclusion by simply looking at the results of Table 1. We do not think we need to give a complex argumentation for this result since it is almost trivial. However, in the new version we point the reader to Table 1 to see this in more detail. }

@@

@@

{\color{blue} Yes, this happens in most soils, but in mangroves bulk densities increase strongly due to hydrostatic pressure. However, we agree in that this sentence is not very relevant for the discussion on differences in bulk density among the two mangrove types.}

@@

@@

{\color{blue} We beg to differ. In this paragraph we do not make any definitive statements as stated by the reviewer. When we use a word such as `likely', we are actually implying that this might be the case, but there is uncertainty. Notice that we use wording such as `this assumption is supported', `this could mean either ... or ...' , 'which would underpin', etc. These are all hedged statements that show our interpretation of the results and our favoring for a specific interpretation, but away from a definite true.}

@@

{\color{blue} Organic C concentrations and total N show a very high correlation among each other (0.96 Pearson correlation coefficient), and the C:N ratio does not differ between the two forest types. Therefore, the information in the total N variable is redundant with respect to the information in organic C. Therefore, we think that adding an analysis of the C:N ratio does not contribute much to the story, as opposed to using other independent variables such as the isotopic composition of carbon, and the mineralogical composition of the sediments. }

>>>>

\opening{Dear Dr. Aseda}
Thank you very much for your consideration of our manuscript and for the opportunity to submit a revised version. We made several changes to the manuscript based on reviewers' comments. Most changes attempt at increasing clarity addressing reviewers' suggestions. In addition, we changed the statistical test used for comparisons, using now a non-parametric test that does not rely on the assumption of normality of the data. For details, see the answers to the comments below.

@@

{\color{blue} We thank the reviewer for recognizing the value of this study and pointing out different issues such as lack of detailed descriptions and confidence in wording. We have made an effort to address all these issues (see answers below), and as a result the manuscript is now much improved. In some cases however, we think some of the issues raised by the reviewer are due to misunderstandings of the text. In these cases, we made an effort to present a more clear text. }

@@

{\color{blue} Habitat and environmental characteristics of the basing and fringe mangroves are described in the Materials and Methods section. Here in the introduction, we are describing the main motivation of the study and therefore it is not the most appropriate place to describe the study site. Figure 1 is mentioned in the text in the Methods section.}

@@

{\color{blue} We added a new paragraph giving this rationale. }

@@

{\color{blue} The rationale is presented now in the introduction, where we mention that we use analyses of the structure and composition of the clay minerals to help in determining the origin of the stored carbon.}

@@

{\color{blue} Sorry for the confusion. In the ANOVA we didn't compare four categorical zones as the reviewer thought, but only the two groups of mangrove types: fringe and basin. Therefore the Tukey post-hoc test is not needed. However, given in the new version of the manuscript we do not use ANOVA anymore for comparisons of means. Since the data was not normally distributed, we use now a Wilcoxon test to compare the distribution of the data. Description of statistical analyses was changed accordingly in the text. }

@@

{\color{blue} This is inferred by simply multiplying bulk density by \% organic carbon. Also, you can reach this conclusion by simply looking at the results of Table 1. We do not think we need to give a complex argumentation for this result since it is almost trivial. However, in the new version we explain this result better and point the reader to Table 1 to see this in more detail. }

@@

{\color{blue} We reworded this paragraph. The point is simply that the results helped us to make an interpretation of the origin of the carbon, but this is analyzed only in the discussion, independent of the results section where se state the result without interpret them. }

@@

{\color{blue} Yes, this happens in most soils, but in mangroves bulk densities increase strongly due to hydrostatic pressure. However, we agree in that this sentence is not very relevant for the discussion on differences in bulk density among the two mangrove types, and therefore we removed it.}

@@

{\color{blue} Some of this information was added to the introduction.}

@@

{\color{blue} We beg to differ. In this paragraph we do not make any definitive statements as stated by the reviewer. When we use a word such as `likely', we are actually implying that this might be the case, but there is uncertainty. Notice that we use wording such as `this assumption is supported', `this could mean either ... or ...' , 'which would underpin', etc. These are all hedged statements that show our interpretation of the results and our favoring for a specific interpretation, but away from a definite true. \\ Despite our disagreement on this matter, we did try to change the language in several parts of the manuscript to make our statements less `definite'.}

@@

{\color{blue} Organic C concentrations and total N show a very high correlation among each other (0.96 correlation coefficient), and the C:N ratio does not differ between the two forest types. Therefore, the information in the total N variable is redundant with respect to the information in organic C. Therefore, we think that adding an analysis of the C:N ratio does not contribute much to the story, as opposed to using other independent variables such as the isotopic composition of carbon, and the mineralogical composition of the sediments. }
